Trap spaces of Boolean networks are conflict-free siphons of their Petri net encoding

### 2023-03-09 manuscripts/TCS2022/tcs2022.tex
Timeout problem of CP and ILP for N-K models

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on the \texttt{PyBoolNet} repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \scalebox{0.9}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & \texttt{LQM} & \texttt{PBN} & \texttt{mpbn} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
    \midrule
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.03 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.01 & 0.00 & 0.01 & - & - & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.03 & 0.02 & 0.03 & - & - & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.03 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & jaoude\_thdiff & 103 & $1000^+$ & N/A & \textbf{0.85} & \textbf{0.45} & \textbf{0.56} & - & - & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & \textbf{0.11} & 0.01 & 0.01 & 0.01 & - & - & 0.02\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{0.11} & \textbf{17.83} & 0.01 & 0.01 & - & - & 0.01\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.01 & - & - & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.01 & \textbf{NM} & 0.00 & - & - & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{0.94} & 0.02 & 0.02 & - & - & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.06 & 0.00 & 0.00 & - & - & 0.02\\
    \rownb & selvaggio\_emt & 56 & $1000^+$ & N/A & \textbf{0.48} & \textbf{0.28} & \textbf{0.28} & - & - & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & - & - & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.09 & 0.09 & 0.07 & - & - & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.04 & 0.08 & 0.11 & - & - & 0.04\\
    \bottomrule
  \end{tabular}
  }
\end{table}
\setcounter{rownumber}{0}

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogxaxis}[
			%title={},
			xlabel={Time (s)},
			ylabel={Models solved},
			xmin=-1, xmax=180,
			log basis x={10},
			%scale only axis,
			ymin=100, ymax=134,
			%ymode=log,
			%log basis y={10},
			xtick={0.5, 1, 2, 5, 10, 20, 50, 100, 180},
			xticklabels = {0.5, 1, 2, 5, 10, 20, 50, 100, 180},
			ytick={100, 110, 120, 130},
			y=0.5cm/4,
			%legend style={font=\fontsize{7}{8}\selectfont},
			%legend style={at={(1.2,-0.1)},anchor=north west},
			legend pos=outer north east,
			ymajorgrids=true,
			grid style=dashed,
		]

@@

%		\addplot[
%			smooth,
%			thick,
%			%dashed,
%			color=green,
%			mark=star,
%		]
%		coordinates {
%			(0.5, 143)(1, 176)(2, 195)(5, 222)(10, 249)(20, 264)(50, 287)(100, 308)(180, 322)
%		}; \addlegendentry{\texttt{CP}}

@@

		%		\addplot[
		%			smooth,
		%			thick,
		%			%dashed,
		%			color=green,
		%			mark=star,
		%		]
		%		coordinates {
		%			(0.5, 143)(1, 176)(2, 195)(5, 222)(10, 249)(20, 264)(50, 287)(100, 308)(180, 322)
		%		}; \addlegendentry{\texttt{CP}}

@@

\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on selected models from the literature.}
  % in bold if greater than or equal to 10
  \centering%
  \label{tab:result_real}
  \scalebox{0.82}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & \texttt{LQM} & \texttt{PBN} & \texttt{mpbn} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
    \midrule % n < 100
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & \textbf{0.10} & 0.04 & NM & 0.01 & - & - & 0.02 \\
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & \textbf{0.10} & 0.06 & NM & 0.01 & - & - & 0.02 \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & \textbf{1.76} & NM & 0.08 & - & - & 0.14 \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.41 & \textbf{1.76} & NM & 0.07 & - & - & 0.14 \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & \textbf{DNF} & \textbf{DNF} & NM & 0.03 & - & - & 0.19 \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & \textbf{0.24} & \textbf{0.33} & NM & 0.02 & - & - & 0.05 \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.17 & 0.57 & \textbf{40.39} & 0.07 & - & - & 0.11 \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & \textbf{DNF} & \textbf{DNF} & NM & 0.16 & - & - & 0.28 \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & 0.43 & NM & 0.07 & - & - & 0.06 \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $1000^+$ & N/A & 0.11 & 0.36 & 0.17 & - & - & 0.06 \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & 0.05 & 0.07 & 0.06 & - & - & 0.05 \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & \textbf{1.29} & \textbf{5.67} & NM & 0.06 & - & - & 0.08 \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $1000^+$ & N/A & \textbf{DNF} & 0.50 & 0.34 & - & - & 0.33 \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & \textbf{39.22} & \textbf{1.01} & 0.20 & 0.12 & - & - & 0.05 \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.23 & 0.04 & 0.08 & 0.06 & - & - & 0.05 \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $1000^+$ & N/A & 0.09 & 0.55 & 0.37 & - & - & 0.15 \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $1000^+$ & N/A & \textbf{107.57} & 0.76 & 0.56 & - & - & 0.16 \\

    \midrule % 100 <= n < 200
     \rownb & Adhesion\_CIP~\cite{guberman2020boolean} & 121 & 78 & \textbf{56.81} & \textbf{4.25} & 0.23 & 0.17 & - & - & 0.19 \\
    \rownb & EMT\_Mech~\cite{Sullivan2022} & 136 & 82 & \textbf{DNF} & \textbf{14.01} & 0.27 & 0.20 & - & - & 0.25 \\
    \rownb & macrophage~\cite{DesignPrinciplesGeneNetworks} & 136 & $1000^+$ & N/A & 0.54 & 1.09 & 0.84 & - & - & 0.27 \\
    \rownb & angiogenesis~\cite{DesignPrinciplesGeneNetworks} & 141 & $1000^+$ & N/A & 0.16 & 1.07 & 1.06 & - & - & 0.16 \\
    \rownb & angiofull~\cite{Weinstein2017} & 142 & $1000^+$ & N/A & 0.17 & 1.06 & 0.88 & - & - & 0.23 \\
    \rownb & EMT\_Mech\_TGFbeta~\cite{Sullivan2022} & 150 & 492 & \textbf{DNF} & \textbf{11.28} & 0.78 & 0.69 & - & - & 0.35 \\
    \rownb & RA\_apoptosis~\cite{aghamiri2020automated} & 180 & $1000^+$ & N/A & \textbf{DNF} & 1.43 & 1.55 & - & - & 0.19 \\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & $1000^+$ & N/A & \textbf{13.58} & 1.76 & 1.51 & - & - & 0.27 \\

    \midrule % 200 <= n
    \rownb & Snf1-pathway~\cite{Lubitz2015} & 202 & $1000^+$ & N/A & 1.13 & 1.47 & 1.43 & - & - & 0.31 \\
    \rownb & T-cell-co-receptor~\cite{DesignPrinciplesGeneNetworks} & 206 & $1000^+$ & N/A & \textbf{DNF} & 1.52 & 2.26 & - & - & 0.35 \\
    \rownb & TcellCheckPoint~\cite{hernandez2020computational} & 218 & $1000^+$ & N/A & \textbf{4.99} & NM & 1.96 & - & - & 0.28 \\
    \rownb & Mycobacterium~\cite{DesignPrinciplesGeneNetworks} & 317 & $1000^+$ & N/A & 0.42 & 2.36 & \textbf{4.91} & - & - & 0.44 \\
    \rownb & Leishmania~\cite{DesignPrinciplesGeneNetworks} & 342 & $1000^+$ & N/A & \textbf{DNF} & 2.56 & \textbf{5.62} & - & - & 0.46 \\
    \rownb & Cholocystokinin~\cite{aghamiri2020automated} & 383 & $1000^+$ & N/A & 0.36 & 2.99 & \textbf{4.81} & - & - & 0.37 \\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & $1000^+$ & N/A & \textbf{DNF} & NM & \textbf{18.21} & - & - & 0.79 \\

>>>>

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on the \texttt{PyBoolNet} repository.}
  \centering%
  \label{tab:pyboolnet_repo}
  \scalebox{0.9}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & \texttt{LQM} & \texttt{PBN} & \texttt{mpbn} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
    \midrule
    \rownb & arellano\_rootstem & 9 & 4 & \textbf{0.13} & 0.01 & 0.00 & 0.00 & \textbf{0.97} & \textbf{0.96} & 0.01\\
    \rownb & calzone\_cellfate & 28 & 27 & \textbf{0.12} & 0.02 & 0.01 & 0.01 & \textbf{5.59} & \textbf{6.03} & 0.01\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & \textbf{0.11} & 0.03 & 0.01 & 0.01 & \textbf{6.56} & \textbf{6.99} & 0.01\\
    \rownb & davidich\_yeast & 10 & 12 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & \textbf{2.56} & \textbf{2.21} & 0.01\\
    \rownb & dinwoodie\_life & 15 & 7 & \textbf{0.11} & 0.01 & 0.00 & 0.01 & \textbf{1.68} & \textbf{1.39} & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{0.39} & \textbf{0.29} & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & \textbf{0.11} & 0.02 & 0.01 & 0.01 & \textbf{0.58} & \textbf{0.46} & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & \textbf{0.19} & 0.03 & 0.02 & 0.03 & \textbf{3.93} & \textbf{10.46} & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & \textbf{0.12} & 0.03 & 0.01 & 0.01 & \textbf{0.37} & \textbf{0.39} & 0.02\\
    \rownb & jaoude\_thdiff & 103 & $1000^+$ & N/A & \textbf{0.85} & \textbf{0.45} & \textbf{0.56} & \textbf{DNF} & \textbf{DNF} & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & \textbf{0.11} & 0.01 & 0.01 & 0.01 & \textbf{1.98} & \textbf{1.22} & 0.02\\
    \rownb & krumsiek\_myeloid & 11 & 6 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{1.48} & \textbf{1.26} & 0.01\\
    \rownb & multivalued & 13 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{0.93} & \textbf{0.86} & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{0.11} & \textbf{17.83} & 0.01 & 0.01 & \textbf{1.21} & \textbf{1.10} & 0.01\\
    \rownb & n3s1c1a & 2 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{0.63} & \textbf{0.49} & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & \textbf{0.09} & 0.02 & 0.00 & 0.00 & \textbf{0.56} & \textbf{0.49} & 0.01\\
    \rownb & n5s3 & 4 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.00 & \textbf{0.74} & \textbf{0.69} & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & \textbf{0.10} & 0.02 & 0.00 & 0.00 & \textbf{0.91} & \textbf{0.59} & 0.01\\
    \rownb & n7s3 & 6 & 3 & \textbf{0.11} & 0.02 & 0.00 & 0.00 & \textbf{0.79} & \textbf{0.68} & 0.01\\
    \rownb & raf & 3 & 2 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{0.55} & \textbf{0.39} & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & \textbf{0.10} & 0.02 & \textbf{NM} & 0.01 & \textbf{0.77} & \textbf{0.67} & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & \textbf{0.10} & 0.01 & \textbf{NM} & 0.00 & \textbf{2.07} & \textbf{1.46} & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{0.15} & \textbf{0.94} & 0.02 & 0.02 & \textbf{5.98} & \textbf{7.98} & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & \textbf{0.10} & 0.06 & 0.00 & 0.00 & \textbf{0.53} & \textbf{0.45} & 0.02\\
    \rownb & selvaggio\_emt & 56 & $1000^+$ & N/A & \textbf{0.48} & \textbf{0.28} & \textbf{0.28} & \textbf{DNF} & \textbf{DNF} & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{0.74} & \textbf{0.75} & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & \textbf{0.10} & 0.01 & 0.00 & 0.00 & \textbf{1.00} & \textbf{0.89} & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & \textbf{0.60} & 0.09 & 0.09 & 0.07 & \textbf{37.26} & \textbf{DNF} & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & \textbf{0.64} & 0.04 & 0.08 & 0.11 & \textbf{69.95} & \textbf{DNF} & 0.04\\
    \bottomrule
  \end{tabular}
  }
\end{table}
\setcounter{rownumber}{0}

@@

\begin{figure}[ht]
	\centering
	\begin{tikzpicture}
		\begin{semilogxaxis}[
			%title={},
			xlabel={Time (s)},
			ylabel={Models solved},
			xmin=-1, xmax=180,
			%xmode=log,
			%log basis x={10},
			%scale only axis,
			ymin=0, ymax=134,
			%ymode=log,
			%log basis y={2},
			xtick={0.5, 1, 2, 5, 10, 20, 50, 100, 180},
			xticklabels = {0.5, 1, 2, 5, 10, 20, 50, 100, 180},
			ytick={0,20,40,60,80,100,120},
			y=0.5cm/10,
			%legend style={font=\fontsize{7}{8}\selectfont},
			%legend style={at={(1.2,-0.1)},anchor=north west},
			legend pos=outer north east,
			ymajorgrids=true,
			grid style=dashed,
		]

@@

		\addplot[
			smooth,
			thick,
			%dashed,
			color=green,
			mark=star,
		]
		coordinates {
			(0.5, 4)(1, 33)(2, 59)(5, 87)(10, 109)(20, 118)(50, 122)(100, 130)(180, 133)
		}; \addlegendentry{\texttt{CP}}

@@

%		\addplot[
%			smooth,
%			thick,
%			%dashed,
%			color=green,
%			mark=star,
%		]
%		coordinates {
%			(0.5, 4)(1, 33)(2, 59)(5, 87)(10, 109)(20, 118)(50, 122)(100, 130)(180, 133)
%		}; \addlegendentry{\texttt{CP}}

@@

\begin{table}[!htb]
  \caption{Timing comparisons (in seconds) between \texttt{bioLQM} (\texttt{LQM}), \texttt{PyBoolNet} (\texttt{PBN}), \texttt{mpbn} and the four variants of \texttt{Trappist} on selected models from the literature.}
  % in bold if greater than or equal to 10
  \centering%
  \label{tab:result_real}
  \scalebox{0.82}{
  \begin{tabular}{rlrrrrrrrrr}
    \toprule
    & & & & & & & \multicolumn{4}{c}{\texttt{Trappist}}\\
    \cmidrule(rr){8-11}
    & model & \(n\) & \(|M|\) & \texttt{LQM} & \texttt{PBN} & \texttt{mpbn} & \texttt{SAT} & \texttt{CP} & \texttt{ILP} & \texttt{ASP} \\
    \midrule % n < 100
    \rownb & metastatic~\cite{DesignPrinciplesGeneNetworks} & 10 & 4 & \textbf{0.10} & 0.04 & NM & 0.01 & \textbf{1.15} & \textbf{0.89} & 0.02 \\
    \rownb & Arabidopsis\_thaliana~\cite{DesignPrinciplesGeneNetworks} & 15 & 8 & \textbf{0.10} & 0.06 & NM & 0.01 & \textbf{2.06} & \textbf{1.83} & 0.02 \\
    \rownb & p53\_high\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.38 & \textbf{1.76} & NM & 0.08 & 0.53 & 0.43 & 0.14 \\
    \rownb & p53\_low\_dna~\cite{DesignPrinciplesGeneNetworks} & 16 & 1 & 0.41 & \textbf{1.76} & NM & 0.07 & 0.58 & 0.48 & 0.14 \\
    \rownb & FT-GRN~\cite{ChvezHernndez2022} & 23 & 32 & \textbf{DNF} & \textbf{DNF} & NM & 0.03 & \textbf{8.41} & \textbf{12.38} & 0.19 \\
    \rownb & DNA\_damage~\cite{DesignPrinciplesGeneNetworks} & 26 & 16 & \textbf{0.24} & \textbf{0.33} & NM & 0.02 & \textbf{3.91} & \textbf{5.33} & 0.05 \\
    \rownb & Rho-GTPases~\cite{DesignPrinciplesGeneNetworks} & 33 & 2 & 0.17 & 0.57 & \textbf{40.39} & 0.07 & \textbf{0.74} & 0.56 & 0.11 \\
    \rownb & Pluripotency~\cite{YachieKinoshita2018} & 36 & 440 & \textbf{DNF} & \textbf{DNF} & NM & 0.16 & \textbf{138.92} & \textbf{DNF} & 0.28 \\
    \rownb & Pluripotent~\cite{DesignPrinciplesGeneNetworks} & 36 & 276 & 0.37 & 0.43 & NM & 0.07 & \textbf{72.40} & \textbf{DNF} & 0.06 \\
    \rownb & Pancreatic\_Cancer~\cite{DesignPrinciplesGeneNetworks} & 43 & $1000^+$ & N/A & 0.11 & 0.36 & 0.17 & \textbf{DNF} & \textbf{DNF} & 0.06 \\
    \rownb & Drosophila~\cite{RodrguezVega2014} & 52 & 128 & 0.33 & 0.05 & 0.07 & 0.06 & \textbf{32.66} & \textbf{126.22} & 0.05 \\
    \rownb & Cacace\_TdevModel~\cite{Cacace2020} & 61 & 28 & \textbf{1.29} & \textbf{5.67} & NM & 0.06 & \textbf{7.51} & \textbf{23.15} & 0.08 \\
    \rownb & hedgehog~\cite{DesignPrinciplesGeneNetworks} & 65 & $1000^+$ & N/A & \textbf{DNF} & 0.50 & 0.34 & \textbf{DNF} & \textbf{DNF} & 0.33 \\
    \rownb & EMT~\cite{Rozum2021} & 69 & 268 & \textbf{39.22} & \textbf{1.01} & 0.20 & 0.12 & \textbf{75.81} & \textbf{DNF} & 0.05 \\
    \rownb & Bcell~\cite{Dutta2019} & 73 & 72 & 0.23 & 0.04 & 0.08 & 0.06 & \textbf{18.95} & \textbf{81.85} & 0.05 \\
    \rownb & mast\_cell~\cite{aghamiri2020automated} & 73 & $1000^+$ & N/A & 0.09 & 0.55 & 0.37 & \textbf{DNF} & \textbf{DNF} & 0.15 \\
    \rownb & Corral\_ThIL17diff~\cite{corral2021interplay} & 92 & $1000^+$ & N/A & \textbf{107.57} & 0.76 & 0.56 & \textbf{DNF} & \textbf{DNF} & 0.16 \\

    \midrule % 100 <= n < 200
     \rownb & Adhesion\_CIP~\cite{guberman2020boolean} & 121 & 78 & \textbf{56.81} & \textbf{4.25} & 0.23 & 0.17 & \textbf{25.20} & \textbf{DNF} & 0.19 \\
    \rownb & EMT\_Mech~\cite{Sullivan2022} & 136 & 82 & \textbf{DNF} & \textbf{14.01} & 0.27 & 0.20 & \textbf{27.55} & \textbf{DNF} & 0.25 \\
    \rownb & macrophage~\cite{DesignPrinciplesGeneNetworks} & 136 & $1000^+$ & N/A & 0.54 & 1.09 & 0.84 & \textbf{DNF} & \textbf{DNF} & 0.27 \\
    \rownb & angiogenesis~\cite{DesignPrinciplesGeneNetworks} & 141 & $1000^+$ & N/A & 0.16 & 1.07 & 1.06 & \textbf{DNF} & \textbf{DNF} & 0.16 \\
    \rownb & angiofull~\cite{Weinstein2017} & 142 & $1000^+$ & N/A & 0.17 & 1.06 & 0.88 & \textbf{DNF} & \textbf{DNF} & 0.23 \\
    \rownb & EMT\_Mech\_TGFbeta~\cite{Sullivan2022} & 150 & 492 & \textbf{DNF} & \textbf{11.28} & 0.78 & 0.69 & \textbf{DNF} & \textbf{DNF} & 0.35 \\
    \rownb & RA\_apoptosis~\cite{aghamiri2020automated} & 180 & $1000^+$ & N/A & \textbf{DNF} & 1.43 & 1.55 & \textbf{DNF} & \textbf{DNF} & 0.19 \\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & $1000^+$ & N/A & \textbf{13.58} & 1.76 & 1.51 & \textbf{DNF} & \textbf{DNF} & 0.27 \\

    \midrule % 200 <= n
    \rownb & Snf1-pathway~\cite{Lubitz2015} & 202 & $1000^+$ & N/A & 1.13 & 1.47 & 1.43 & \textbf{DNF} & \textbf{DNF} & 0.31 \\
    \rownb & T-cell-co-receptor~\cite{DesignPrinciplesGeneNetworks} & 206 & $1000^+$ & N/A & \textbf{DNF} & 1.52 & 2.26 & \textbf{DNF} & \textbf{DNF} & 0.35 \\
    \rownb & TcellCheckPoint~\cite{hernandez2020computational} & 218 & $1000^+$ & N/A & \textbf{4.99} & NM & 1.96 & \textbf{DNF} & \textbf{DNF} & 0.28 \\
    \rownb & Mycobacterium~\cite{DesignPrinciplesGeneNetworks} & 317 & $1000^+$ & N/A & 0.42 & 2.36 & \textbf{4.91} & \textbf{DNF} & \textbf{DNF} & 0.44 \\
    \rownb & Leishmania~\cite{DesignPrinciplesGeneNetworks} & 342 & $1000^+$ & N/A & \textbf{DNF} & 2.56 & \textbf{5.62} & \textbf{DNF} & \textbf{DNF} & 0.46 \\
    \rownb & Cholocystokinin~\cite{aghamiri2020automated} & 383 & $1000^+$ & N/A & 0.36 & 2.99 & \textbf{4.81} & \textbf{DNF} & \textbf{DNF} & 0.37 \\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & $1000^+$ & N/A & \textbf{DNF} & NM & \textbf{18.21} & \textbf{DNF} & \textbf{DNF} & 0.79 \\
